Develop atlantisom wrappers

### 2020-01-17 WrapperDevelopment.Rmd
dont need extra surveyconfig function

@@

om_index <- function(surveyconfig = survey_configfile, 
                     fisheryconfig = fishery_configfile, 
                     omlist_ss = omlist_ss, 
                     n_reps = n_reps,
                     save = TRUE){

  #configure the independent survey, a default census is in config/survcensus.R
  #survey configuration must specify survey time, area, efficiency (q), selectivity
  #survey species inherited from omlist_ss
  source(surveyconfig)

@@

  #configure the fishery, a default is in config/fisherycensus.R
  #fishery configuration must specify survey time, area, efficiency (q), selectivity
  #fishery species inherited from omlist_ss
  source(fisheryconfig)

}

@@

CC3om_sard_ind <- om_index(surveyconfig = here("config/survcensus.R"), 
                           fisheryconfig = "",
                           omlist_ss = CC3om_sardine, 
                           n_reps = 5, 
                           save = FALSE)

>>>>

The hardcoded script omdimensions.R needs to sit in the atlantisom config folder.

@@

om_index <- function(usersurvey = usersurvey_file, 
                     userfishery = userfishery_file, 
                     omlist_ss, 
                     n_reps = n_reps,
                     save = TRUE){

  #one script for dimension parameters to be used in multiple functions
  source("config/omdimensions.R", local = TRUE)

  # user options for survey--default is a census with mid-year sample
  source(usersurvey, local = TRUE)

@@

  #configure the fishery, a default is in config/fisherycensus.R
  #fishery configuration must specify survey time, area, efficiency (q), selectivity
  #fishery species inherited from omlist_ss
  source(userfishery, local = TRUE)

  #we are not currently subsetting fishery catch because we cannot correct catch.nc
  #  instead the catch in biomass from catch.txt is read in for the index
  #  we do not apply any cv to this, but we could this way (default cv=0)

  fishObsCatchB <- list()
  for(i in 1:n_reps){
    fishObsCatchB[[i]] <- atlantisom::sample_fishery_totcatch(omlist_ss$truecatchbio_ss, fish_cv)
  }

  if(save){
    saveRDS(fishObsCatchB, file.path(d.name, paste0(scenario.name, "fishCatch.rds")))
  }

  indices <- list("survObsBiomB" = survObsBiomB,
                  "fishObsCatchB" = fishObsCatchB)

  return(indices)
}

@@

CC3om_sard_ind <- om_index(usersurvey = here("config/usersurvey.R"), 
                           userfishery = here("config/fisherycensus.R"),
                           omlist_ss = CC3om_sardine, 
                           n_reps = 5, 
                           save = TRUE)
